---
title: "SciDB Util"
author: "Alber Sanchez"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---



The `scidbutil` package provides a set of utlitary functions for working with multidimensional arrays of Earth observation data hosted in [SciDB](http://scidb.org/). This vignette is meant to introduce users to some usage examples.



## Coordinate transformation: WGS84 to MODIS sinusoidal

MODIS uses a [synusoidal projection](https://en.wikipedia.org/wiki/Sinusoidal_projection) to spatially represent their [data](https://code.env.duke.edu/projects/mget/wiki/SinusoidalMODIS). The SR-ORG code of this projection is [6974](http://spatialreference.org/ref/sr-org/6974/).

A common task while working with MODIS data is to transform coordinates from and to MODIS sinusoidal projection. Below, we present the case of [WGS84](https://en.wikipedia.org/wiki/WGS84).


```{r}
library(sp)

# create the coordinate systems
proj4326 <- "+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs"
proj_modis_sinusoidal <- "+proj=sinu +lon_0=0 +x_0=0 +y_0=0 +a=6371007.181 +b=6371007.181 +units=m +no_defs"

# create a matrix of points
x <- c(-56.239700, -56.325531)
y <- c(-11.623990, -11.676781)
lonlat.mat <- cbind(x, y)

# build spatial-points
S <- SpatialPoints(lonlat.mat)
proj4string(S) <-CRS(proj4326)

# transform to MODIS sinusoidal
modis.sp <- spTransform(S, CRS(proj_modis_sinusoidal))

# transform back to WGS84
(wgs84.sp <- spTransform(modis.sp, CRS(proj4326)))
```


## Coordinate transformation: WGS84 to SciDB column and row

Now, we need to obtain the position of a pixel in the array and we have the pixel's  [WGS84](https://en.wikipedia.org/wiki/WGS84) coordinates. In other words, we need to transform from longitude and latitude to `col_id` and `row_id`.

```{r}
library(scidbutil)

# calculate the size of a MODIS pixel
pixelSize <- calcPixelSize(4800, calcTileWidth())

# do the coordinate transformation
(res <- wgs84gmpi(lonlat.mat, pixelSize))
```


## Transform time ids into dates

The `scidbutil` package also provides functions to transform from and to time reference systems.


```{r}
tid <- 0:2
MOD13Q1.period <- 16 
(date.vector <- time_id2date(time_id.vector = tid, period = MOD13Q1.period))
```
